---
title: "STT810 ICA4"
author: "Tiancheng Liu"
date: "2022-09-15"
output:
  word_document:
    toc: yes
    toc_depth: '3'
  html_document:
    toc: yes
    toc_depth: 3
    number_sections: yes
    theme: united
    highlight: tango
    css: my.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Question 1

### a

cdf(x = 1) = 0.3 (probability x ≤ 1)
cdf(x = 2) = 0.5 (probability x ≤ 2)
cdf(x = 3) = 0.65 (probability x ≤ 3)
cdf(x = 4) = 1 (probability x ≤ 4)


### b

4*4 = 16 total outcome

the possible outcome 4 has combination 1+3, 2+2, 2+2 and 3+1

So it's "0.3*0.15*2 + 0.2*0.2" = 0.13

We can also test with R function.

```{r}
lis <- (sample(c(1:4),10000,prob = c(0.3,0.2,0.15,0.35),replace = T) + sample(c(1:4),10000,prob = c(0.3,0.2,0.15,0.35),replace = T))

sum(lis == 4)/10000
```

We can see it's similiar.

## Question 2

### a



```{r}
dbinom(6,12,0.5)
```


We can see it's 0.22556.

```{r}
pbinom(3,12,0.5)
```

We can see the probability for the coin is heads 3 times or less is 0.073.

### c

```{r}
sample(c(0,1),12,replace = T)
```


## Question 3

### a

```{r}
1-pbinom(1,6,0.2)
```

The probability is 0.345.

### b

```{r}
dbinom(0, 6, 0.2)
```

The probability of winning 0 times out of 6 is 0.262.

### c

```{r}
xx = replicate(10000,sample(c(1:5),6,replace = T))


tes <- 0
for (i in 1:10000){
  if ((sum(xx[,i]==1) == 0)){
    tes <- tes + 1
  }
}
tes/10000
```

We can see that the results are simular.

